### 2023-02-25 frontmatter/notation.tex
Add benchmarking paper

% Notation entries
\nomenclature[A, 01]{$a$}{A scalar; integer or real}
\nomenclature[A, 02]{$\a$}{A column vector}
\nomenclature[A, 03]{$\A$}{A matrix}
\nomenclature[A, 04]{$\text{diag}(\a)$}{A square diagonal matrix of the elements of $\a$}
\nomenclature[A, 05]{$\e$}{A vector of ones, $\e=\bmat{1 & \cdots & 1}\transpose$}
\nomenclature[A, 06]{$\I$}{The identity matrix, $\I=\text{diag}\pa{\e}$}

@@

\nomenclature[C, 01]{$a_i$}{Element $i$ of vector $\a$ with first index $1$}
\nomenclature[C, 02]{$A_{i,j}$}{Element $i,j$ of matrix $\A$. Comma omitted when unambiguous.}
\nomenclature[C, 03]{$A_{i,:}$}{Row $i$ of matrix $\A$ (a row vector)}
\nomenclature[C, 04]{$A_{:,j}$}{Column $j$ of matrix $\A$ (a column vector)}
\nomenclature[C, 05]{$\a^\bra{l}$}{Neural network layer indexing; a vector in layer $l$}
\nomenclature[C, 06]{$\a^\vbra{t}$}{Recurrent neural network sequence indexing; vector at timestep $t$ in sequence $\cbra{\a^\vbra{t}}_{t=1}^T$}

\nomenclature[D, 01]{$\a\transpose$}{Transpose of column vector $\a$ to give row vector}
\nomenclature[D, 02]{$\A\transpose$}{Transpose of matrix $\A$}
\nomenclature[D, 03]{$\a\transpose\b$}{Inner product of $\a$ and $\b$, $\a\transpose\b=\a\cdot\b$}
\nomenclature[D, 04]{$\a\b\transpose$}{Outer product of $\a$ and $\b$}
\nomenclature[D, 05]{$\A\B$}{Matrix product of $\A$ and $\B$}
\nomenclature[D, 06]{$\A*\B$}{Convolution (actually cross-correlation) of $\A$ and $\B$}
\nomenclature[D, 07]{$\A\odot\B$}{Elementwise, or Hadamard, product of $\A$ and $\B$}
\nomenclature[D, 08]{$\det{\A}$}{Determinant of matrix $\A$}
\nomenclature[D, 09]{$\norm{\a}$}{$L^2$ norm of $\a$}
\nomenclature[D, 10]{$\norm{\a}_p$}{$L^p$ norm of $\a$}
\nomenclature[D, 11]{$\Tr{\A}$}{Trace of matrix $\A$, $\Tr{\A}=\sum_i A_{i,i}$}

\nomenclature[E, 01]{$\frac{\text{d}y}{\text{d}x}$}{Derivative of $y$ with respect to $x$}
\nomenclature[E, 02]{$\pd{y}{x}$}{Partial derivative of $y$ with respect to $x$}
\nomenclature[E, 03]{$\nabla_\x$}{Del, nabla or Laplacian operator, $\nabla_\x = \bmat{\pd{}{x_1} & \cdots & \pd{}{x_n}}^\text{T}, \; \x\in\mathbb{R}^{n}$}
\nomenclature[E, 04]{$\nabla_\x y$}{Gradient of $y$ with respect to $\x$, $\nabla_\x y = \bmat{\pd{y}{x_1} & \cdots & \pd{y}{x_n}}^\text{T}, \; \x\in\mathbb{R}^{n}$}
\nomenclature[E, 05]{$\H_\x$}{Hessian operator, $\H_\x = \nabla_\x\nabla_\x\transpose = \bmat{
	    \pd[2]{}{x_1} & \frac{\partial^2}{\partial x_1 \partial x_2} & \cdots & \frac{\partial^2}{\partial x_1 \partial x_n}\\
	    \frac{\partial^2}{\partial x_2 \partial x_1} & \pd[2]{}{x_2} & \cdots & \frac{\partial^2}{\partial x_2 \partial x_n}\\
	    \vdots & \vdots & \ddots & \vdots\\
	    \frac{\partial^2}{\partial x_n \partial x_1} & \frac{\partial^2}{\partial x_n \partial x_2} & \cdots & \pd[2]{}{x_n}
	    }$}
\nomenclature[E, 06]{$\H_\x y$}{Hessian matrix of $y$ with respect to $\x$; matrix of all second order partial derivatives}
\nomenclature[E, 07]{$\nabla^2_\x$}{Laplacian operator, $\nabla^2_\x=\nabla_\x\transpose\nabla_\x = \nabla_\x\cdot\nabla_\x=\sum_i \pd[2]{}{x_i}=\Tr{\H_\x}$}
\nomenclature[E, 08]{$\nabla^2_\x y$}{Laplacian of $y$ with respect to $\x$; sum of the unmixed second order partial derivatives}
\nomenclature[E, 09]{$\pd{\y}{\x}$}{Jacobian matrix of $\y$ w.r.t. $\x$, $\pd{\y}{\x} = \bmat{
	    \nabla_\x y_1 &
	    \cdots &
	    \nabla_x y_n}^\text{T}, \; \y\in\mathbb{R}^{n}$; matrix of all possible first order partial derivatives}
\nomenclature[E, 10]{$\int f(\x)\,\text{d}\x$}{Definite integral over the domain of $\x$}
\nomenclature[E, 11]{$\int_\mathcal{D} f(\x)\,\text{d}\x$}{Definite integral over the domain $\mathcal{D}$}

\nomenclature[F, 01]{$a\sim p$}{$a$ is a random variable with distribution $p$}
\nomenclature[F, 02]{$\text{E}\bra{f(x)}$}{Expectation of $f(x)$ with respect to $p(x)$; sometimes also $\text{E}\bra{f(x)}_{x\sim p(x)}$}
\nomenclature[F, 03]{$\text{Var}\bra{f(x)}$}{Variance of $f(x)$ under $p(x)$}
\nomenclature[F, 04]{$\text{Cov}\bra{f(x), g(x)}$}{Covariance of $f(x)$ and $g(x)$ under $p(x)$}
\nomenclature[F, 05]{$D_\text{KL}\pa{p\mid\mid q}$}{Kullback-Leibler divergence of $p$ and $q$}
\nomenclature[F, 06]{$D_\text{KL}\pa{p,q}$}{Symmetrized Kullback-Leibler divergence of $p$ and $q$}
\nomenclature[F, 07]{$\mathcal{N}\pa{\x\mid\mub,\Sigmab}$}{Gaussian distribution over $\x$ with mean $\mub$ and covariance $\Sigmab$}

>>>>

% Notation entries
\nomenclature[A, 01]{$a$}{A scalar; integer or real}
\nomenclature[A, 02]{$\ab$}{A column vector}
\nomenclature[A, 03]{$\Ab$}{A matrix}
\nomenclature[A, 04]{$\text{diag}(\ab)$}{A square diagonal matrix of the elements of $\ab$}
\nomenclature[A, 05]{$\e$}{A vector of ones, $\e=\bmat{1 & \cdots & 1}\transpose$}
\nomenclature[A, 06]{$\Ib$}{The identity matrix, $\Ib=\text{diag}\pa{\e}$}

@@

\nomenclature[C, 01]{$a_i$}{Element $i$ of vector $\ab$ with first index $1$}
\nomenclature[C, 02]{$A_{i,j}$}{Element $i,j$ of matrix $\Ab$. Comma omitted when unambiguous.}
\nomenclature[C, 03]{$A_{i,:}$}{Row $i$ of matrix $\Ab$ (a row vector)}
\nomenclature[C, 04]{$A_{:,j}$}{Column $j$ of matrix $\Ab$ (a column vector)}
\nomenclature[C, 05]{$\ab^\bra{l}$}{Neural network layer indexing; a vector in layer $l$}
\nomenclature[C, 06]{$\ab^\vbra{t}$}{Recurrent neural network sequence indexing; vector at timestep $t$ in sequence $\cbra{\ab^\vbra{t}}_{t=1}^T$}

\nomenclature[D, 01]{$\ab\transpose$}{Transpose of column vector $\ab$ to give row vector}
\nomenclature[D, 02]{$\Ab\transpose$}{Transpose of matrix $\Ab$}
\nomenclature[D, 03]{$\ab\transpose\bb$}{Inner product of $\ab$ and $\bb$, $\ab\transpose\bb=\ab\cdot\bb$}
\nomenclature[D, 04]{$\ab\bb\transpose$}{Outer product of $\ab$ and $\bb$}
\nomenclature[D, 05]{$\Ab\Bb$}{Matrix product of $\Ab$ and $\Bb$}
\nomenclature[D, 06]{$\Ab*\Bb$}{Convolution (actually cross-correlation) of $\Ab$ and $\Bb$}
\nomenclature[D, 07]{$\Ab\odot\Bb$}{Elementwise, or Hadamard, product of $\Ab$ and $\Bb$}
\nomenclature[D, 08]{$\det{\Ab}$}{Determinant of matrix $\Ab$}
\nomenclature[D, 09]{$\norm{\ab}$}{$L^2$ norm of $\ab$}
\nomenclature[D, 10]{$\norm{\ab}_p$}{$L^p$ norm of $\ab$}
\nomenclature[D, 11]{$\Tr{\Ab}$}{Trace of matrix $\Ab$, $\Tr{\Ab}=\sum_i A_{i,i}$}

\nomenclature[E, 01]{$\frac{\text{d}y}{\text{d}x}$}{Derivative of $y$ with respect to $x$}
\nomenclature[E, 02]{$\pd{y}{x}$}{Partial derivative of $y$ with respect to $x$}
\nomenclature[E, 03]{$\nabla_\xb$}{Del, nabla or Laplacian operator, $\nabla_\xb = \bmat{\pd{}{x_1} & \cdots & \pd{}{x_n}}^\text{T}, \; \xb\in\mathbb{R}^{n}$}
\nomenclature[E, 04]{$\nabla_\xb y$}{Gradient of $y$ with respect to $\xb$, $\nabla_\xb y = \bmat{\pd{y}{x_1} & \cdots & \pd{y}{x_n}}^\text{T}, \; \xb\in\mathbb{R}^{n}$}
\nomenclature[E, 05]{$\H_\xb$}{Hessian operator, $\H_\xb = \nabla_\xb\nabla_\xb\transpose = \bmat{
	    \pd[2]{}{x_1} & \frac{\partial^2}{\partial x_1 \partial x_2} & \cdots & \frac{\partial^2}{\partial x_1 \partial x_n}\\
	    \frac{\partial^2}{\partial x_2 \partial x_1} & \pd[2]{}{x_2} & \cdots & \frac{\partial^2}{\partial x_2 \partial x_n}\\
	    \vdots & \vdots & \ddots & \vdots\\
	    \frac{\partial^2}{\partial x_n \partial x_1} & \frac{\partial^2}{\partial x_n \partial x_2} & \cdots & \pd[2]{}{x_n}
	    }$}
\nomenclature[E, 06]{$\H_\xb y$}{Hessian matrix of $y$ with respect to $\xb$; matrix of all second order partial derivatives}
\nomenclature[E, 07]{$\nabla^2_\xb$}{Laplacian operator, $\nabla^2_\xb=\nabla_\xb\transpose\nabla_\xb = \nabla_\xb\cdot\nabla_\xb=\sum_i \pd[2]{}{x_i}=\Tr{\H_\xb}$}
\nomenclature[E, 08]{$\nabla^2_\xb y$}{Laplacian of $y$ with respect to $\xb$; sum of the unmixed second order partial derivatives}
\nomenclature[E, 09]{$\pd{\y}{\xb}$}{Jacobian matrix of $\y$ w.r.t. $\xb$, $\pd{\y}{\xb} = \bmat{
	    \nabla_\xb y_1 &
	    \cdots &
	    \nabla_x y_n}^\text{T}, \; \y\in\mathbb{R}^{n}$; matrix of all possible first order partial derivatives}
\nomenclature[E, 10]{$\int f(\xb)\,\text{d}\xb$}{Definite integral over the domain of $\xb$}
\nomenclature[E, 11]{$\int_\mathcal{D} f(\xb)\,\text{d}\xb$}{Definite integral over the domain $\mathcal{D}$}

\nomenclature[F, 01]{$a\sim p$}{$a$ is a random variable with distribution $p$}
\nomenclature[F, 02]{$\text{E}\bra{f(x)}$}{Expectation of $f(x)$ with respect to $p(x)$; sometimes also $\text{E}\bra{f(x)}_{x\sim p(x)}$}
\nomenclature[F, 03]{$\text{Var}\bra{f(x)}$}{Variance of $f(x)$ under $p(x)$}
\nomenclature[F, 04]{$\text{Cov}\bra{f(x), g(x)}$}{Covariance of $f(x)$ and $g(x)$ under $p(x)$}
\nomenclature[F, 05]{$D_\text{KL}\pa{p\mid\mid q}$}{Kullback-Leibler divergence of $p$ and $q$}
\nomenclature[F, 06]{$D_\text{KL}\pa{p,q}$}{Symmetrized Kullback-Leibler divergence of $p$ and $q$}
\nomenclature[F, 07]{$\mathcal{N}\pa{\xb\mid\mub,\Sigmab}$}{Gaussian distribution over $\xb$ with mean $\mub$ and covariance $\Sigmab$}
